Millions of Type Errors

### 2023-09-04 programming23/paper.tex
negative edit range note

Edit range ignore huge numbers (above 4 billion),
which are the result of subtraction overflowing.
%% 4,000,000,000

@@

>>>>

Edit ranges are negative in a handful of records (1,533).
%% out/negative-edit-range.txt
%% actual value is NOT negative, but large positive over 4 billion
%% example: 4294967293
This may happen when a user deletes a large block of code.
Since the issue affects so few records, we omit those ranges
from the analysis.

@@

\appendix

\section{Data Details}

Tips for interpreting the data:

\begin{itemize}
  \item
    Edit ranges are non-negative because we
    implemented the interval arithmetic for them using unsigned integers.
    To filter out negative edit ranges, we removed all ranges
    greater than 4 billion.

  \item
  \item
  \item
\end{itemize}
